\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{setspace}

\title{CS2050 Summer 2022 Homework 1 Solutions}
\author{Due: May 25}
\date{Released: May 18}

\newcommand{\pt}[1]{\textcolor{blue}{(#1 points)}}

\newcommand{\pte}[1]{\textcolor{blue}{(#1 points each)}}

\newenvironment{solution_draft} {
    \par
    \color{blue}
    \textbf{Solution:}
} {
    \par
}

\newenvironment{rubric}
{
\par
\begin{spacing}{.6}
\begin{itshape}
\color{red}

}
{
\end{itshape}
\end{spacing}
\par
}

\begin{document}

\maketitle

This assignment is due on \textbf{11:59 PM EST, Wednesday, May 25, 2022}.  On-time submissions receive 3\% extra credit. You may turn it in one day late for 5\% penalty or two days late for a 15\% penalty. Assignments more than two days late will NOT be accepted.  We will prioritize on-time submissions when grading before an exam. \\ 

You should submit a typeset or \emph{neatly} written pdf on Gradescope.  The grading TA should not have to struggle to read what you've written; if your handwriting is hard to decipher, you will be required to typeset your future assignments.\\ 

You may collaborate with other students, but any written work should be your own. Write the names of the students you work with on the top of your assignment.\\

Always justify your work, even if the problem doesn't specify it. It can help the TA's to give you partial credit.



\clearpage

\begin{enumerate}

    \item Rewrite each of the following in the form "if ...., then ...".  (You may adjust verb tense as you wish to make the sentences sound natural.) \pt 6
    
    \begin{enumerate}
        \item It is necessary for you to perform a rain dance so that it rains on Tuesday.
        
        \item You can come to my birthday party only if you buy me cake.
        
        \item A sufficient condition for you to become head TA is that you defeat the current head TA in hand-to-hand combat.
    \end{enumerate}

    
    \begin{solution}
    \begin{enumerate}
    \item[(a)] If it rained on Tuesday, then you performed a rain dance.
    \item[(b)] If you came to my birthday party, then you bought me a cake.
    \item[(c)] If you defeat the current head TA in hand-to-hand combat, then you can become head TA.
    \end{enumerate}
    \end{solution}
    
    \item Evaluate each of the following propositions as True or False. \pt 8
    \begin{enumerate}
        \item If squares have four sides, then triangles have five sides.
        \item If $7 \geq 7$, then $0 > -1$.
        \item If $6+2 = 19$, then $2+6=91$.
        \item If $5$ is not odd, then $4$ is not odd. 
    \end{enumerate}
    
    \begin{solution}
    \begin{enumerate}
        \item \textbf{F}
        \item \textbf{T}
        \item \textbf{T}
        \item \textbf{T}
    \end{enumerate}
    \end{solution}
    
    \item Let $s$ be the proposition ``You eat sushi.", let $h$ be the proposition "You hang out with your fiends.", and let $f$ be the proposition "It is Friday." Expressing the following as English sentences. (Again, you may adjust tense as you like.) \pt 6
    
    \begin{enumerate}
        \item $f \rightarrow s$
        \item $\lnot f \wedge (h \vee s)$
    \end{enumerate}
    
    \begin{solution}
    \begin{enumerate}
        \item If it is Friday, then you eat sushi.
        \item It is not Friday and you hang out with your friends or you eat sushi.
    \end{enumerate}
    \end{solution}
    
    \item Let $l$ be the proposition ``You are late for class.", let $o$ be the proposition ``You oversleep", and let $c$ be the proposition ``You charge your phone." Represent each of the following statements using only $l, o, c$ and logical operators. \pt 6
    
    \begin{enumerate}
        \item You oversleep only when you do not charge your phone.
        \item You are late for class unless you charge your phone and do not oversleep.
    \end{enumerate}
    
    \begin{solution}
    \begin{enumerate}
        \item $o \rightarrow \neg c$
        \item $l \rightarrow (c \land \neg o)$
    \end{enumerate}
    \end{solution}
    
    \item Give the converse, contrapositive, and inverse of the statement ``I get ice cream whenever I finish my homework." (Don't worry about tense, just get the idea correct.) \pt 6
    
    \begin{solution}\\
    Preliminary translation: "if I finish my homework, I get ice cream."
    \begin{enumerate}
        \item \textbf{Converse:} If I get ice cream, then I (will) finish my homework. 
        \item \textbf{Contrapositive:} If I didn't get ice cream, then I didn't finish my homework.
        \item \textbf{Inverse:} If I don't get ice cream, then I won't finish my homework.
    \end{enumerate}
    \end{solution}
    
    \item Construct truth tables for the following propositions. Include all intermediate columns, in an appropriate order, for full credit. \pte 8
    
    \begin{enumerate}
        \item $p \rightarrow \lnot q$
        \item $p \vee (q \wedge \lnot r)$
        
        \item $(p \vee q) \leftrightarrow \lnot (p \wedge q)$
    \end{enumerate}
    
    \begin{solution}
    \begin{enumerate}
        \item
            \begin{tabular}{c|c|c|c}
                $p$ & $q$ & $\neg q$ & $p \rightarrow \neg q$  \\
                \hline
                T & T & F & F\\
                T & F & T & T\\
                F & T & F & T\\
                F & F & T & T\\
            \end{tabular}
        \item 
            \begin{tabular}{c|c|c|c|c|c}
                $p$ & $q$ & $r$ & $\neg r$ & $q \land \neg r$ & $p \lor (q \land \neg r)$\\
                \hline
                T & T & T & F & F & T \\
                T & T & F & T & T & T \\
                T & F & T & F & F & T \\
                T & F & F & T & F & T \\
                F & T & T & F & F & F \\
                F & T & F & T & T & T \\
                F & F & T & F & F & F \\
                F & F & F & T & F & F \\
            \end{tabular}
        \item
            \begin{tabular}{c|c|c|c|c}
                $p$ & $q$ & $p \lor q$ & $p \land q$ & $\neg (p \land q)$ \\
                \hline
                T & T & T & T & T\\
                T & F & T & F & F\\
                F & T & T & F & F\\
                F & F & F & F & T\\
            \end{tabular}
    \end{enumerate}
    \end{solution}
    
    \item Simplify each of the following to $p$, $q$, $T$ or $F$ using logical equivalences. State the equivalence used at each step. \pte 8
    
    \begin{enumerate}
        \item $p \rightarrow (p \vee q)$
        \item $((\lnot p \rightarrow \lnot q) \rightarrow q)$
        \item $(p \rightarrow q) \wedge (p \rightarrow \lnot q)$. (Hint: equivalences can be used in both ``directions".)
    \end{enumerate}
    
    \begin{solution}
    \begin{enumerate}
        \item \begin{tabular}{c|c}
            $p \rightarrow (p \lor q)$ & Premise \\
            $\neg p \lor (p \lor q)$ & Material Implication \\
            $(\neg p \lor p) \lor q$ & Associative Law \\
            $(p \lor \neg p) \lor q$ & Commutative Law \\
            $T \lor q$ & Negation Law \\
            $q \lor T$ & Commutative Law \\
            $T$ & Domination Law \\
        \end{tabular}
        \item \begin{tabular}{c|c}
            $((\lnot p \rightarrow \lnot q) \rightarrow q)$ & Premise \\
            $(\neg(\lnot p \rightarrow \lnot q) \lor q)$ & Material Implication \\
            $(\neg(\neg \neg p \lor \neg q) \lor q)$ & Material Implication \\
            $(\neg(p \lor \neg q) \lor q)$ & Double Negation\\
            $(\neg p \land \neg \neg q) \lor q)$ & DeMorgan's Law\\
            $(\neg p \land q) \lor q$ & Double Negation\\
            $q \lor (\neg p \land q)$ & Commutative\\
            $q \lor (q \land \neg p)$ & Commutative\\
            $q $ & Absorption\\
        \end{tabular}
        \item
        \begin{tabular}{c|c}
            $(p \rightarrow q) \land (p \rightarrow \neg q)$ &  Premise\\
            $(\neg p \lor q) \land (p \rightarrow \neg q)$ &  Material Implication\\
            $(\neg p \lor q) \land (\neg p \lor \neg q)$ &  Material Implication\\
            $\neg p \lor (q \land \neg q)$ & Distributive Law\\
            $\p \lor F$ & Negation\\
            $\neg p$ & Identity
        \end{tabular}
    \end{enumerate}
    \end{solution}
    
    
    \item Prove that $p\rightarrow(p\wedge q) \equiv (p \rightarrow q)$ in both of the following ways.
    \begin{enumerate}
        \item truth table \pt{10}
        \item logical equivalences \pt{10}
    \end{enumerate}
    \begin{solution}
    \begin{enumerate}
        \item \begin{tabular}{c|c|c|c|c}
             $p$ & $q$ & $p \land q$ & $p \rightarrow q$ & $p \rightarrow (p \land q)$ \\
             \hline
             T & T & T & T & T\\
             T & F & F & F & F\\
             F & T & F & T & T\\
             F & F & F & T & T\\
        \end{tabular} \\
        Thus, Col4 = Col5 $\rightarrow [(p\wedge q) \equiv (p \rightarrow q)]$
        \item \begin{tabular}{c|c}
             $p \rightarrow (p \land q)$ & RHS \\
             $\neg p \lor (p \land q)$ & Material Implication\\
             $(\neg p \lor p) \land (\p \lor q)$ & Distributive Law\\
             $(p \lor \neg p) \land (\p \lor q)$ & Commutative Law\\
             $T \land (\neg p \lor q)$ & Negation\\
             $\neg p \lor q$ & Identity \\
             $p \rightarrow q$ & Material Implication
             \end{tabular}
        \end{enumerate}
    \end{solution}
    
    
\end{enumerate}

\end{document}