\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{setspace}

\usepackage{amsmath, amssymb, amsthm}


\title{CS 2050 Fall 2022 Homework 3}
\author{Due: September 16}
\date{Released: September 9}

\newcommand{\pt}[1]{\textcolor{blue}{(#1 points)}}

\newcommand{\pte}[1]{\textcolor{blue}{(#1 points each)}}

\newenvironment{solution}
{
\par
\color{blue}
\textbf{Solution:}
}
{
\par
}

\newenvironment{rubric}
{
\par
\begin{spacing}{.6}
\begin{itshape}
\color{red}

}
{
\end{itshape}
\end{spacing}
\par
}

\begin{document}

\maketitle

This assignment is due on \textbf{11:59 PM EST, Friday, September 9, 2022}.  On-time submissions receive 2.5 points of extra credit. You may turn it in one day late for a 10 point penalty or two days late for a 25 point penalty. Assignments more than two days late will NOT be accepted.  We will prioritize on-time submissions when grading before an exam. \\ 

You should submit a typeset or \emph{neatly} written pdf on Gradescope.  The grading TA should not have to struggle to read what you've written; if your handwriting is hard to decipher, you will be required to typeset your future assignments.\\ 

You may collaborate with other students, but any written work should be your own. Write the names of the students you work with on the top of your assignment.\\

Always justify your work, even if the problem doesn't specify it. It can help the TA's to give you partial credit.
\\

Author(s): David Teng, Richard Zhao

\clearpage

\begin{enumerate}
    \item Prove or disprove that $\sqrt[3]{2}$ is irrational, given that $a^n + b^n = c^n$ is always false for any 3 integers a,b and c when $n > 2$. \pt{10}
    
    \item{Let $n$ be an integer. Prove the statement ``If $3n^3 + 2n + 4$ is even, then $n$ is even." Make sure to include the introduction, body, and conclusion. Clearly state your reasoning for all statements and use a two-column proof for the body whenever possible.\hfill\hfill \color{blue}(5 points each)}
    \begin{enumerate}
        \item[a)] Prove the statement using a proof by contrapositive.
        \item[b)] Prove the statement using a proof by contradiction.
    \end{enumerate}

    \item{$a_0 = 1, a_1 = 4, a_2 = 16, a_4 = 64, a_{t} = a_{t-1} + a_{t-2} + a_{t-3} + a_{t-4}, t \in \mathbb{Z}^{\geq 4}$. Prove or disprove that $a_n \leq 4^n$ for all $n \geq 0$.}
    
    \item Let s be the sum of 5 distinct positive perfect squares. Prove or disprove that if s is odd, then at least one of these 5 integers in its sum must be odd.
    
    \item Prove or disprove that given 2 integers $x$ and $y$, if $x^2 + y^2$ is even, then $x + y$ is also even.
    
    % Sarthak (nevermind i didn't know it was in rosen)
    
    % Prove the \textbf{triangle inequality}, which states that if $x, y \in \mathbb{R}$, then $|x| + |y| \ge |x + y|$. Here, $|x|$ is the absolute value of $x$ defined as
    % $$|x|=
    % \begin{cases}
    %     x & \text{if } x \ge 0 \\
    %     -x & \text{if } x< 0
    % \end{cases}$$
    % \textit{Hint: break the proof up into cases, considering all possible choices of $x$ and $y$ being positive, negative, or zero.}
    
\end{enumerate}

\end{document}
