% One-page, ATS-friendly LaTeX resume + cover letter (Automation Genesis — Discrete Engineering Track)
% Replace all bracketed placeholders [like this] with your personal details.
\documentclass[11pt]{article}
\hbadness=10000                       % Suppress Warnings (Horizontal)
\vbadness=10000                       % Suppress Warnings (Vertical)
\usepackage[margin=0.7in]{geometry}
\usepackage{parskip}          % better spacing between paragraphs
\usepackage{enumitem}         % control list spacing
\usepackage[hidelinks]{hyperref}
\usepackage{helvet}

% Compact list spacing
\setlist[itemize]{leftmargin=*,itemsep=2pt,topsep=2pt}
\setlist[enumerate]{leftmargin=*,itemsep=2pt,topsep=2pt}

\begin{document}

% https://ibmglobal.avature.net/en_US/careers/JobDetail?jobId=54830&source=SN_LinkedIn
% https://ibmglobal.avature.net/en_US/careers/JobDetail?jobId=56285&source=SN_LinkedIn

\section*{Software Engineer - Fullstack at Microsoft}

As a Software Engineer, the individual will develop software, tools, and 
code to be used in support of design, infrastructure, and technology 
platforms as well as commercial or end-user applications. This role involves 
creating and implementing extensible and maintainable code, partnering with 
stakeholders to determine user requirements, and assuring the quality of 
solutions through testing, debugging, and monitoring telemetry.

\section*{Software Engineering by \textbf{Microsoft}}
\textbf{Job number:} 1885860. This is a general, remote (US-based) 
application for a full-stack individual contributor role (IC2), 
focusing on a broad range of software development tasks across 
Microsoft's products and services. The company emphasizes a culture of 
\textbf{``learn-it-alls rather than know-it-alls.''}

\begin{itemize}
  \item \textbf{Field:} Software Engineering
  \item \textbf{Pay range (IC2):} \$84,200 -- \$165,200 annually (USD). 
    (Note: SF Bay area and NYC metro range is \$109,000 -- \$180,400).
  \item \textbf{Benefits:} Details referenced at the Microsoft corporate pay 
    page: \url{https://careers.microsoft.com/us/en/us-corporate-pay}
  \item \textbf{Employment type:} Full-Time, Remote (0 days / week 
    in-office), Individual Contributor
  \item \textbf{Locations:} Multiple Locations, United States (Remote)
  \item Posted on \textbf{Oct 01, 2025} (Accepting applications until 
    Oct 31, 2025)
  \begin{enumerate}[label=\arabic*., leftmargin=*]
    \item \textbf{Experience required}: Proven experience coding in 
      languages (C, C++, C\#, Java, JavaScript, or Python).
    \item \textbf{Education}: Bachelor's Degree (or currently pursuing) 
      in Computer Science or related technical discipline, OR equivalent 
      experience.
    \item \textbf{Support}: This is a remote role; relocation is not 
      applicable.
    \item \textbf{Travel}: 0--25\%.
  \end{enumerate}
\end{itemize}

\section*{Career Path}
Microsoft emphasizes a culture centered around a \textbf{growth mindset} 
and values of respect, integrity, and accountability. This role is an 
\textbf{Individual Contributor (IC2)} position, suggesting a role for 
an engineer who is beyond entry-level and is capable of taking ownership 
(acting as a DRI) of features and services, contributing to design, and 
collaborating with stakeholders, while continuously learning.

\newpage
\subsection*{Core responsibilities}
\begin{itemize}
  \item Review and break down work items, provide estimations, and 
    support safe feature deployments.
  \item Collaborate with key stakeholders to define feature requirements 
    and integrate feedback for continuous improvement.
  \item Learn and apply coding standards and best practices through code 
    reviews; develop maintainable and extensible code.
  \item Utilize debugging tools, logs, and telemetry to proactively and 
    reactively address issues in product features.
  \item Support the identification of dependencies and contribute to 
    design documentation and architectural processes.
  \item Collaborate on quality assurance plans, augment test cases, and 
    integrate automation into testing.
  \item Act as a \textbf{Designated Responsible Individual (DRI)} for 
    monitoring and restoring system functionality within Service Level 
    Agreement (SLA) timeframes.
  \item Participate in live service operations and support telemetry data 
    integration for insights into system behavior.
  \item Ensure compliance with security, privacy, safety, and 
    accessibility standards.

  \item \hrulefill
  
  \item \textbf{Required Qualifications:}
  \begin{itemize}
    \item Bachelor's Degree (or currently pursuing) in Computer Science 
      or related technical discipline, OR equivalent experience.
    \item Proven experience coding in languages including, but not limited 
      to, C, C++, C\#, Java, JavaScript, or Python.
  \end{itemize}
  
  \item \textbf{Preferred Qualifications:}
  \begin{itemize}
    \item Bachelor's Degree in CS/related field AND 1+ year(s) technical 
      engineering experience (with specified languages).
    \item OR Master's Degree (or currently pursuing) in CS/related field 
      with coding experience (with specified languages).
  \end{itemize}
  
  \item \hrulefill
  \item \textbf{Growth Mindset:} A cultural attribute at Microsoft 
    referring to the belief that abilities and intelligence can be 
    developed through dedication, effort, and learning from failure, 
    rather than being fixed traits.
  \item \textbf{Designated Responsible Individual (DRI):} A role common 
    in live-site service operations where one person is the on-call 
    point of contact responsible for monitoring a service and 
    coordinating the response to any incidents (e.g., outages) to 
    restore functionality.
  \item \textbf{Telemetry:} Data collected from remote sources (like 
    running software or services) used to monitor system behavior, 
    performance, health, and usage patterns.
  \item \textbf{IC2 (Individual Contributor 2):} A Microsoft engineering 
    level (often equivalent to L60 or L61) that is above entry-level 
    (IC1/L59) and represents a core software engineer who can work 
    independently on features.
\end{itemize}

In this role, the engineer is responsible for the full software 
development lifecycle—from requirements gathering and coding to testing, 
deployment, and live site operations—while adhering to Microsoft's 
cultural values of growth, respect, and accountability.


\end{document}