\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{setspace}
\usepackage{algpseudocode}
\usepackage{mathtools}

\usepackage{enumitem}

\usepackage{amsmath, amssymb, amsthm}


\title{CS 2050 Fall 2022 Homework 9}
\author{Due: November 4}
\date{Released: November 11}

\newcommand{\pt}[1]{\textcolor{blue}{(#1 points)}}

\newcommand{\pte}[1]{\textcolor{blue}{(#1 points each)}}

\newenvironment{solution}
{
\par
\color{blue}
\textbf{Solution:}
}
{
\par
}

\newenvironment{rubric}
{
\par
\begin{spacing}{.6}
\begin{itshape}
\color{red}

}
{
\end{itshape}
\end{spacing}
\par
}

\begin{document}

\maketitle

\begin{enumerate}
    \item[i.] This assignment is due on \textbf{11:59 PM EST, Friday, November 11, 2022}.  On-time submissions receive 2.5 points of extra credit. You may turn it in one day late for a 10 point penalty or two days late for a 25 point penalty. Assignments more than two days late will NOT be accepted.  We will prioritize on-time submissions when grading before an exam.
    \item[ii.] You will submit your assignment on \textbf{Gradescope}. Shorter answers may be entered directly into response fields, however longer answer must be recorded on a typeset (e.g. using \LaTeX) or \emph{neatly} written PDF.
    \item[iii.] Ensure that all questions are correctly assigned on Gradescope. Questions that take up multiple pages should have all pages assigned to that question. Incorrect page assignments can lead to point deductions.
    \item[iv.] You may collaborate with other students, but any written work should be your own. Write the names of the students you work with on the top of your assignment.
    \item[v.] Always justify your work, even if the problem doesn't specify it. It can help the TA's to give you partial credit.
\end{enumerate}

Author(s): David Teng, Richard Zhao, Sarthak Mohanty, Rohan Bodla
\newpage
\begin{enumerate}

\item Show that a three-dimensional $2^n$ × $2^n$ × $2^n$ checkerboard with one 1 × 1 × 1 cube missing can be completely filled by 2 × 2 × 2 cubes with one 1 × 1 × 1 cube removed. \pt{25}

%\item Prove that $\sqrt[x]{2}$ is irrational, for all integers $x > 2$. You can use the fact that $a^n + b^n = c^n$ is always false for any 3 integers a,b and c when $n > 2$.

\item Given sets $A_1, A_2, A_3, ..., A_n$ that are a part of a universal set $U$, prove  that $\overline{A_1 \cup A_2 \cup A_3 \cup ... \cup A_n} = \overline{A_1} \cap \overline{A_2} \cap \overline{A_3} \cap ... \cap \overline{A_n}$.  \pt{25}

% perhaps add this to the next hw.
% \item Use strong induction to show that the square root of 28 is irrational. You must use strong induction to receive credit on this problem.

\item Find the smallest integer value $x$ such that you can form postage of $x$ cents and greater using only 6 cent and 11 cent stamps. Use strong induction to prove that your identified value of x is a valid choice. \pt{25}

\item Suppose you have the sequence which is recursively defined as follows:\\
\\$a_0 = 1$
\\$a_1 = 4$
\\$a_2 = 16$
\\$a_t = a_{t-1}+ a_{t-2} + a_{t-3}$, where $t \in \mathbb{Z}^{\geq 3}$\\
\\Using strong induction, prove that $a_n \leq 4^n$ for all $n \geq 0$. \pt{25}



\end{enumerate}
\end{document}

