\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{amsfonts}

\title{CS2050 Summer 2022 Homework 5}
\author{Due: June 29}
\date{Released: June 22}

\newcommand{\pt}[1]{\textcolor{blue}{(#1 points)}}

\newcommand{\pte}[1]{\textcolor{blue}{(#1 points each)}}
\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}

\newenvironment{solution}
{
\par
\color{blue}
\textbf{Solution:}
}
{
\par
}

\newenvironment{rubric}
{
\par
\begin{spacing}{.6}
\begin{itshape}
\color{red}

}
{
\end{itshape}
\end{spacing}
\par
}

\begin{document}

\maketitle

This assignment is due on \textbf{11:59 PM EST, Wednesday, June 29, 2022}.  On-time submissions receive 3\% extra credit. You may turn it in one day late for 5\% penalty or two days late for a 15\% penalty. Assignments more than two days late will NOT be accepted.  We will prioritize on-time submissions when grading before an exam. \\ 

You should submit a typeset or \emph{neatly} written pdf on Gradescope.  The grading TA should not have to struggle to read what you've written; if your handwriting is hard to decipher, you will be required to typeset your future assignments.\\ 

You may collaborate with other students, but any written work should be your own. Write the names of the students you work with on the top of your assignment.\\

Always justify your work, even if the problem doesn't specify it. It can help the TA's to give you partial credit.



\clearpage
\begin{enumerate}



\item Let $a,b,c,d \in \mathbb{Z}$, where $a \neq 0$ and $b \neq 0$. Prove that if $a|c$ and $b|d$, then $ab|cd$. \pt{10}

\begin{rubric}
-4, doesn't cite definition of divisibility

-4, doesn't cite algebra/manipulation

-2, no conclusion
\end{rubric}

\item Solve for $x$ in the following congruences. Show your work for full credit. \pte{5}
\begin{enumerate}
    \item $12 \equiv x \Mod{5}$, $0 \leq x \leq 10$
    \item $12 \equiv 5 \Mod{x}$, $0 \leq x \leq 10$
    \item $5x \equiv 3\Mod{11}$, $0 \leq x \leq 10$
    \item $71^2 + 14^4 \equiv x\Mod{9}$, $0 \leq x < 9$
\end{enumerate}

\begin{rubric}
-2, arithmetic error

-4, no work shown

-5, incorrect
\end{rubric}

\item Convert each of the following decimal integers into their binary, hexadecimal, and octal expansions. Show your work for full credit. \pte{10}
\begin{enumerate}
    \item 27
    \item 2050
\end{enumerate}

\begin{rubric}
-3, incorrect binary

-3, incorrect hexadecimal

-3, incorrect octal

-2, error propagation (binary to hex/octal)
\end{rubric}

\item Find the prime factorization of each of the following integers. \pte{4}
\begin{enumerate}
    \item 9072
    \item 324
    \item 6!
\end{enumerate}

\begin{rubric}
    -4, AON
\end{rubric}

\item Find the greatest common multiple and least common divisor of each of the following pairs of integers. \pte{4}
\begin{enumerate}
    \item $2^4 ∗3^3 ∗5^6$, $2^5 ∗3^3 ∗5^27^2$
    \item $2^47$, $5^513$
\end{enumerate}

\begin{rubric}
    -4, AON
\end{rubric}

\item Write $\gcd(64,12)$ as a linear combination of 64 and 12 by first using the Euclidean algorithm to find the greatest common divisor, then find the bezout coefficients. \pt{15}


\begin{rubric}
    -15, doesn't use Euclidean algorithm
    
    -8, doesn't back-substitute to find Bezout coefficients
    
    -6, error in Euclidean algorithm/airthmetic
    
    
\end{rubric}

\item Prove that $f(x) = 2x^3 + 3x^2 + x\log{x}$ is $O(x^3)$. Show your work using witnesses for full credit. \pt{15}
\begin{rubric}
-10, doesn't use witnesses

-5, doesn't establish inequality

-2, arithmetic/logical error

-2, no conclusion
\end{rubric}

\end{enumerate}

\end{document}
