\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{setspace}

\title{CS2050 Fall 2022 Homework 2}
\author{Due: September 9}
\date{Released: September 2}

\newcommand{\pt}[1]{\textcolor{blue}{(#1 points)}}

\newcommand{\pte}[1]{\textcolor{blue}{(#1 points each)}}

\newenvironment{solution}
{
\par
\color{blue}
\textbf{Solution:}
}
{
\par
}

\newenvironment{rubric}
{
\par
\begin{spacing}{.6}
\begin{itshape}
\color{red}

}
{
\end{itshape}
\end{spacing}
\par
}

\newcommand{\T}{\color{black} \textbf{T}}
\newcommand{\F}{\color{red} \textbf{F}}

\begin{document}

\maketitle

This assignment is due on \textbf{11:59 PM EST, Friday, September 9, 2022}.  On-time submissions receive 2.5 points of extra credit. You may turn it in one day late for a 10 point penalty or two days late for a 25 point penalty. Assignments more than two days late will NOT be accepted.  We will prioritize on-time submissions when grading before an exam. \\ 

You should submit a typeset or \emph{neatly} written pdf on Gradescope.  The grading TA should not have to struggle to read what you've written; if your handwriting is hard to decipher, you will be required to typeset your future assignments.\\ 

You may collaborate with other students, but any written work should be your own. Write the names of the students you work with on the top of your assignment.\\

Always justify your work, even if the problem doesn't specify it. It can help the TA's to give you partial credit.
\\

Author(s): David Teng, Richard Zhao, Nithya Jayakumar

\clearpage

\begin{enumerate}
    \item Knights and Knaves: Each person can either be a Knight or a Knave. A knight always tells the truth and a knave always lies. For the following, determine the roles of Person A, Person B, and Person C or write “Cannot be determined” for that person if there is not enough information. Explain your reasoning for full credit! (You can use a truth table or just plain English to explain.) \pt{11}
    \begin{enumerate}
        \item A says: I am a knave or B is a knight.
        \item B says: C is a knight if A is a knave.
        \item C says: if A is a knave, then B is a knave.
    \end{enumerate}
    
    \begin{solution}
    
    p = A is a knight,
    q = B is a knight,
    r = C is a knight.
    
    
        \begin{tabular}{c|c|c|c|c|c|c|c|c|c|c}
            $p$ & $q$ & $r$ & $\neg p$ & \neg q$ & $\neg p \lor q$ & $p \leftrightarrow \neg p \lor q$ & $\neg p  \rightarrow r$ & $q \leftrightarrow (\neg p \rightarrow r)$ & $\neg p \rightarrow \neg q$ & $r \leftrightarrow (\neg p \rightarrow \neg q)\\
            \hline
            \T & \T & \T & \F & \F & \T & \T & \T & \T & \T & \T\\
            \T & \T & \F & \F & \F & \T & \T & \T & \T & \T & \F\\
            \T & \F & \T & \F & \T & \F & \F & \T & \F & \T & \T\\
            \T & \F & \F & \F & \T & \F & \F & \T & \F & \T & \F\\
            \F & \T & \T & \T & \F & \T & \F & \T & \T & \F & \F\\
            \F & \T & \F & \T & \F & \T & \F & \F & \F & \F & \T\\
            \F & \F & \T & \T & \T & \T & \F & \T & \F & \T & \T\\
            \F & \F & \F & \T & \T & \T & \F & \F & \T & \T & \F\\
        \end{tabular}
        
        
    \\ A: Knight \\
    B: Knight \\
    C: Knight \\
    \end{solution}

    \item Express each of these statements using predicates and quantifiers.\pt{4}
    \begin{enumerate}
        \item[a)] All farmers own cows.\\

        Let the domain for x be the set containing all people and the domain of y being the set containing all animals.\\
        Let $F(x)$: $x$ is a farmer.\\
        Let $C(y)$: $y$ is a cow.\\
        Let $O(x, y)$: $x$ owns $y$.\\
        \begin{solution} \\
        $\forall x(F(x) \rightarrow \exists y (C(x) \land O(x, y)))$
        \end{solution}
        
        \\\\

        
        \item[b)] Some monkeys eat bananas.\\

        Let the domain for x be the set containing all animals.\\
        Let $M(x)$: $x$ is a monkey.\\
        Let $B(x)$: $x$ eats bananas.\\
        
        \begin{solution}
        $\exists x (M(x) \land B(x))$
        \end{solution}
        
        \item[c)] All squares are rectangles, but not all rectangles are squares.\\
        
        Let the domain for x be the set containing all polygons.\\
        Let $S(x)$: $x$ is a square.\\
        Let $R(x)$: $x$ is a rectangle.\\
        
        \begin{solution}
        $\forall x (S(x) \rightarrow R(x)) \land \exists x(R(x) \land \lnot S(x))$
        \end{solution}

    \end{enumerate}
    
    \item Determine the truth value of each of these statements if the domain of each variable consists of all real numbers. \pt{4}
    \begin{enumerate}
        \item[a)] $\exists x \forall y((y = x^2) \rightarrow x + y > y)$\
        \begin{solution}
        true
        \end{solution}\\
        \item[b)] $\forall y \exists x (x/y > 0)$\
        \begin{solution}
        false
        \end{solution}\\
        
        \item[c)] $\forall x \exists y((\sqrt[3]{x} \neq y^2) \rightarrow (x \geq 0))$\
        
        \begin{solution}
        false
        \end{solution}\\
        
        \item[d)] $\exists x \forall y(y > 0 \rightarrow x^y \geq y)$\
        
        \begin{solution}
        true
        \end{solution}
    \end{enumerate}
    
    \item Rewrite each of these statements so that no negation is to the left of a quantifier, so that every negation is immediately to the left of a predicate (in other words, push the negation in past the quantifiers). \pt{6}\\
    \begin{enumerate}
        \item[a)] $\forall x \neg \exists y \forall z (P(x, y) \lor (\lnot G(y) \land S(y, z)))$
        \begin{solution}
        $\forall x \forall y \exists z (\neg P(x, y) \land (G(y) \lor \neg S(y, z)))$
        \end{solution}
        \item[b)] $\neg \forall x (( \exists y A(x, y) \rightarrow \exists y B(x, y)) \rightarrow \neg \exists y C(x, y)) $
        \begin{solution}
        $\exists x (( \forall y \neg A(x, y) \lor \exists y B(x, y)) \land \exists y C(x, y))$
        \end{solution}
        \item[c)] $\neg  \exists y \forall x (R(x,y) \leftrightarrow \exists z S(z,y))$
        \begin{solution}
        $\forall y \exists x ((R(x, y) \lor \forall z \neg S(z, y)) \land (\exists z S(z, y)) \land \neg R(x,y))$
        \end{solution}
        
    \end{enumerate}
    
    
    \item Show that $\neg \forall x \exists y ((A(x) \rightarrow B(y)) \lor (C(x, y) \rightarrow B(y)))$ is logically equivalent to $\exists x \forall y ((A(x) \land C(x, y)) \land \neg B(y))$ \pt{10}\\
    \begin{solution}
    \begin{tabular}{c|c}
        Statement & Reason \\
        \hline
        $\neg \forall x \exists y [(A(x) \rightarrow B(y)) \lor (C(x, y) \rightarrow B(y))]$ & Premise \\
        $\exists x \neg \exists y [(A(x) \rightarrow B(y)) \lor (C(x, y) \rightarrow B(y))]$ & DeMorgan's Law \\
        $\exists x \forall y \neg [(A(x) \rightarrow B(y)) \lor (C(x, y) \rightarrow B(y))] $ & DeMorgan's Law \\
        $\exists x \forall y \neg [(\neg A(x) \lor B(y)) \lor (\neg C(x, y) \lor B(y)]$ & Conditional Disjunction Equivalence \\
        $\exists x \forall y \neg [(\neg A(x) \lor \neg C(x,y)) \lor (B(y) \lor B(y)]$ & Commutativity \& Associativity \\
        $\exists x \forall y \neg [(\neg A(x) \lor \neg C(x,y)) \lor (B(y)]$ & Idempotent Law \\
        $\exists x \forall y [\neg (\neg A(x) \lor \neg C(x,y)) \land \neg (B(y)]$ & DeMorgan's Law \\
        $\exists x \forall y [(\neg \neg A(x) \land \neg \neg C(x,y)) \land \neg (B(y)]$ & DeMorgan's Law \\
        $\exists x \forall y [(A(x) \land C(x,y)) \land \neg (B(y)]$ & Double Negation Law \\
    \end{tabular}
    Thus, using logical equivalences we  have proven that $\neg \forall x \exists y ((A(x) \rightarrow B(y)) \lor (C(x, y) \rightarrow B(y))) \equiv \exists x \forall y ((A(x) \land C(x, y)) \land \neg B(y))$.
    \end{solution}
    
    \item Let $P(x)$ be the statement ``x has a pet pig," let $D(x)$ be the statement ``x has a dog," let $C(x)$ be the statement ``x has a cat," and let $A(x)$ be the statement ``x is allergic to animals." Express each of these statements in terms of $P(x)$, $D(x)$, $C(x)$, $A(x)$, quantifiers, and logical connectives. Let the domain consist of all people.\pt{6}
    \begin{enumerate}
        \item[a)] Any person with allergies cannot own pigs, dogs, or cats.
        \begin{solution}
        $\forall x (A(x) \rightarrow \neg (P(x) \lor D(x) \lor C(x)))$
        \end{solution}
        \item[b)] No one owns all three animals, but everyone owns a pig.
        \begin{solution}
        $\neg \exists x (P(x) \land D(x) \land C(x)) \land \forall x (P(x))$
        \end{solution}
        \item[c)] Each type of animal (cat, pig, and dog) is owned by at least one person.
        \begin{solution}
        $\exists x \exists y \exists z (P(x) \land D(x) \land C(x))$
        \end{solution}
    \end{enumerate}
    
    \item{Find a counterexample, if possible, to these universally quantified statements, where the domain for all variables consists of all real numbers. Otherwise, state that no counterexample exists. \pt{5}}
    \begin{enumerate}
        \item $\forall x (x^{-x} \leq x^x)$
        \begin{solution}
        Anything between 0 and 1 disproves.
        \end{solution}
        \item $\forall x \exists y (y = \frac{x^3}{5})$
        \begin{solution}
        Yes this works
        \end{solution}
        \item $\forall x \forall y  ((y \leq x) \to (x^{16} > y))$
        \begin{solution}
        Wonky values between 0-1 where x and y are very close to 1 but not there disprove.
        \end{solution}
    \end{enumerate}
\end{enumerate}



\end{document}