\begin{enumerate}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #1
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \item Rewrite each of the following in the form "if ...., then ...".  (You may adjust verb tense as you wish to make the sentences sound natural.) \pt 6
    \begin{enumerate}
        \item It is necessary for you to perform a rain dance so that it rains on Tuesday.
        \item You can come to my birthday party only if you buy me cake.
        \item A sufficient condition for you to become head TA is that you defeat the current head TA in hand-to-hand combat.
    \end{enumerate}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{rubric}
        -2 each, AON (All Or Nothing)
    \end{rubric}
    

    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #2
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \item Evaluate each of the following propositions as True or False. \pt 8
    \begin{enumerate}
        \item If squares have four sides, then triangles have five sides.
        \item If $7 \geq 7$, then $0 > -1$.
        \item If $6+2 = 19$, then $2+6=91$.
        \item If $5$ is not odd, then $4$ is not odd. 
    \end{enumerate}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{rubric}
        -2 each, AON
    \end{rubric}


    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #3
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \item Let $s$ be the proposition ``You eat sushi.", let $h$ be the proposition "You hang out with your fiends.", and let $f$ be the proposition "It is Friday." Expressing the following as English sentences. (Again, you may adjust tense as you like.) \pt 6
    \begin{enumerate}
        \item $f \rightarrow s$
        \item $\lnot f \wedge (h \vee s)$
    \end{enumerate}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{rubric}
        -3 each, AON
    \end{rubric}


    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #4
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \item Let $l$ be the proposition ``You are late for class.", let $o$ be the proposition ``You oversleep", and let $c$ be the proposition ``You charge your phone." Represent each of the following statements using only $l, o, c$ and logical operators. \pt 6
    \begin{enumerate}
        \item You oversleep only when you do not charge your phone.
        \item You are late for class unless you charge your phone and do not oversleep.
    \end{enumerate}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{rubric}
        -3 each, AON
    \end{rubric}


    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #5
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \item Give the converse, contrapositive, and inverse of the statement ``I get ice cream whenever I finish my homework." (Don't worry about tense, just get the idea correct.) \pt 6
    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{rubric}
        -3 each, AON
    \end{rubric}


    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #6
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \item Construct truth tables for the following propositions. Include all intermediate columns, in an appropriate order, for full credit. \pte 8
    \begin{enumerate}
        \item $p \rightarrow \lnot q$
        \item $p \vee (q \wedge \lnot r)$
        \item $(p \vee q) \leftrightarrow \lnot (p \wedge q)$
    \end{enumerate}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{rubric}
        -2 per missing/extra/incorrect column\\
        -1 per incorrect cell in a correct column\\
        -2 at least one column to the left of a column it depends on (i.e. $\lnot (p \wedge q)$ to the left of $p \wedge q$).\\
        -1 used 0/1 instead of T/F\\    
        Notes: the book gives a truth table for $\leftrightarrow$, so it is okay if they do not make separate columns for the two unidirectional conditionals.
    \end{rubric}


    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #7
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \item Simplify each of the following to $p$, $q$, $T$ or $F$ using logical equivalences. State the equivalence used at each step. \pte 8
    \begin{enumerate}
        \item $p \rightarrow (p \vee q)$
        \item $((\lnot p \rightarrow \lnot q) \rightarrow q)$
        \item $(p \rightarrow q) \wedge (p \rightarrow \lnot q)$. (Hint: equivalences can be used in both ``directions".)
    \end{enumerate}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{rubric}
        -1 per incorrect/missing/uncited step\\
        QUESTION: are students required to go from $\lnot p \vee p$ to $p \vee \lnot p$ before negation? What about from $T \vee p$ to $p \vee T$ before domination?
    \end{rubric}


    
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #8
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \item Prove that $p\rightarrow(p\wedge q) \equiv (p \rightarrow q)$ in both of the following ways.
    \begin{enumerate}
        \item truth table \pt{10}
        \item logical equivalences \pt{10}
    \end{enumerate}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{rubric}
    TRUTH TABLE\\
    -2 per incorrect/missing column\\
    -1 per incorrect cell in a correct column\\
    -2 at least one column to the left of a column it depends on (i.e. $\lnot (p \wedge q)$ to the left of $p \wedge q$).\\
    -1 used 0/1 instead of T/F\\
    -2 no indication of why the table proves the tautology (just circling columns is sufficient).\\
    LOGICAL EQUIVALENCIES\\
    -1 per incorrect/missing/uncited step\\
    -2 no conclusion\\
    \end{rubric}
\end{enumerate}