\begin{enumerate}







    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #1
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%








    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #2
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%





    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #3
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%





    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #4
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%





    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #5
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%





    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #6
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%





    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #7
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%





    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #8
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%





    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Question #9
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Rubric %%%%%%%%%%%%%%%%%%%%%%%%%%%%





    
\item Given the sets: 
\begin{align*}
    A &:= \{1,8,27,64,125\}\\
    B &:= \{1,16,81,256,635\}\\
    C &:= \{x^2 | x \in \mathbb{Z}\}\
\end{align*}
Find each of the following. You may use set builder notation if necessary.
\pte 5

\begin{enumerate}
    \item $B \cap C$
    \item $A-(B-C)$
    \item $A \cap \emptyset$
    \item $(A \cap B) \times B$
    \item $|\mathcal{P}(B\cap C)|$
\end{enumerate}

\begin{rubric}
-1, per missing element

-2, per incorrect element

\end{rubric}

\item Determine whether the following statements are true or false. \pte{3}

\begin{enumerate}
    \item $\emptyset \in \emptyset$
    \item $\emptyset \subset \emptyset$
    \item $\{\emptyset\} \in \{\emptyset,\{\emptyset\}\}$
    \item $|\{\{\emptyset\}\}| \leq |\{\{\emptyset\}, \{\emptyset\}\}|$
    \item $\mathcal{P}(\emptyset) \subseteq \emptyset$
\end{enumerate}

\begin{rubric}
-3, AON
\end{rubric}

\item Given sets $A$, $B$, and $C$, prove the first distributive law for sets using logical equivalences:   \pt{10}
\begin{center}
    $A \cup (B \cap C) = (A \cup B) \cap (A \cup C)$
\end{center}

\begin{rubric}
-5, fails to reference conjunction or disjunction (and/or)

-5, missing direction ($x \in $ LHS or $x \in $ RHS) for set equality

-1, per skipped/missing steps

-2, missing conclusion
\end{rubric}

\item Let $f$ and $g$ be functions such that: \pte{5}
\begin{align*}
    f(x) &= \lceil x \rceil, \text{where } f : \mathbb{R} \rightarrow \mathbb{Z}\\
    g(x) &= x+1, \text{where } g : \mathbb{Z} \rightarrow \mathbb{R}
 \end{align*}

Determine whether the following function compositions are one-to-one, onto, both, or neither. Justify your reasoning for full credit.

\begin{enumerate}
    \item $(f \circ g)(x)$
    \item $(g \circ f)(x)$
\end{enumerate}

\begin{rubric}
    -2, doesn't check one to one
    
    -2, doesn't check onto
    
    -2 fails to reference function domains
\end{rubric}

\item For each of the following functions from $\mathbb{R}^+ \rightarrow \mathbb{R}$, find the least integer $n$ such that $f(x)$ is $O(x^n)$ if possible. If not, explain why the function is not $O(x^n)$ for any $n$. \pte{5}

\begin{enumerate}
    \item $f(x) = x^{\sqrt{2}}$
    \item $f(x) = 3x^2 + x^3\log(3x^2)$
    \item $f(x) = \frac{x^5 + x^4}{x^9 + x^6\log9x}$
    \item $f(x) = \log x^{\log x}$
\end{enumerate}

\item Use sequence notation to represent each of the following sequences in two ways: as a closed form expression, and then as a recurrence relation (and initial condition). \pte{2}

\begin{enumerate}
    \item 9, 12, 15, 18, 21...
    \item 1, 1, 1, 1, 1...
    \item 3, 15, 75, 375, 1875...
\end{enumerate}

\begin{rubric}
    -2 each, AON
\end{rubric}

\item Evaluate the following sums. Show your work by expanding the terms. \pte{2}

\begin{enumerate}
    \item $\sum_{n=1}^{4} \frac{n(n-1)}{n}$
    \item $\sum_{x=1}^{3} 3^x$
    \item $\sum_{j=0}^{2} \sum_{i=0}^{j} 2^{-i}$
\end{enumerate}

\begin{rubric}
    -2, did not expand terms
    
    -2, incorrect
    
    -1, arithmetic error
\end{rubric}

\item Give pseudocode for finding the average of the positive numbers in a list. \pt{4}

\begin{rubric}
-2, invalid pseudocode

-2, algorithm is slower than $O(n)$
\end{rubric}

\item Consider a function that, given a list of integers, first computes the sum of the elements, then the product, and then averages those two numbers together. The function skips the first element of each list during every iteration by starting the index at 1 outside of the loop. \pte{4}
\begin{enumerate}
    \item Give pseudocode for this algorithm.
    \item What is the runtime of your algorithm?
    \item Given the list $l = [5,3,8,9,2,3,1]$, what will the be output?
\end{enumerate}

\begin{rubric}
-2, incorrect indexing (bounding error)

-4, invalid pseudocode

-4, algorithm is slower than $O(n)$

-4, arithmetic error
\end{rubric}

\item (Extra Credit) Let $A$, $B$, and $C$ be sets. The inclusion-exclusion principle for two sets states that $|A \cup B| = |A| + |B| - |A \cap B|$. Use the inclusion-exclusion principle for two sets to find $|A \cup B \cup C|.$ \pt{1}

\item (Extra Credit) Let $S$ be the set containing all sets which do not contain themselves. Does $S$ contain itself? Show that the answer to this questions leads to a contradiction. \pt{1}

\item (Extra Credit) Determine where there exists a bijection $f : \mathbb{Z} \rightarrow \mathbb{Z}^+$. \pt{1}

\end{enumerate}