% One-page, ATS-friendly LaTeX resume + cover letter (Automation Genesis — Discrete Engineering Track)
% Replace all bracketed placeholders [like this] with your personal details.
\documentclass[11pt]{article}
\hbadness=10000                       % Suppress Warnings (Horizontal)
\vbadness=10000                       % Suppress Warnings (Vertical)
\usepackage[margin=0.7in]{geometry}
\usepackage{parskip}          % better spacing between paragraphs
\usepackage{enumitem}         % control list spacing
\usepackage[hidelinks]{hyperref}
\usepackage{helvet}

% Compact list spacing
\setlist[itemize]{leftmargin=*,itemsep=2pt,topsep=2pt}
\setlist[enumerate]{leftmargin=*,itemsep=2pt,topsep=2pt}

\begin{document}









\section*{Automation Genesis --- Discrete Engineering Track at Siemens}

The \textbf{``Automation Genesis — Discrete Engineering Track''} is identified as 
an 18-month immersive talent development program (full-time, paid) by Siemens.
\begin{itemize}
  \item \textbf{6-Month Intensive Onboarding:} initial phase, work on projects to build a strong foundation in the Siemens automation portfolio.
  \item \textbf{12-Month Development Phase:} development phase, rotation through different functional areas, work on real customer projects, and the design of technical solutions under the guidance of senior engineers.
\end{itemize}

\section*{Discrete automation by \textbf{Siemens Industry, Inc.}}
\textbf{Discrete automation} in Siemens' Digital Industries Automation division is concerned with the manufacturing of individual, countable
items (e.g., automobiles, electronics, or appliances)

\begin{itemize}
  \item \textbf{Field:} Internal Services / Industrial Automation
  \item \textbf{Pay range:} \$81,000 -- \$84,000 annually (actual offer depends on candidate experience, location, and budget).
  \item \textbf{Benefits:} Health and wellness plans; details referenced at the Siemens benefits page: \url{https://www.benefitsquickstart.com/siemens/index.html}
  \item \textbf{Employment type:} Office / Site only, Full-time, permanent, Entry-level
  \item \textbf{Locations:} Mason, OH (first 6 months); then Alpharetta, GA; Elk Grove Village, IL; and/or Harleysville, PA
  \item Start on \textbf{June 8, 2026}, Mason, OH (first 6 months) 
  \begin{enumerate}[label=\arabic*., leftmargin=*]
    \item 6-month intensive onboarding: instructor-led training + hands-on projects.
    \item 12-month development phase: deepen portfolio expertise, customer engagement, and practical engineering experience.
    \item Transition to a designated full-time role, typically as an Engineer on the Technical Consultant team.
    \item \textbf{Support}: Relocation assistance provided for moves $>$ 50 miles.
    \item \textbf{Travel}: project-dependent; typically 5--10\% in light periods, up to 50\% in busier periods.
  \end{enumerate}
\end{itemize}


\section*{Career Path}
Participants are typically placed into full-time positions such as:
\begin{itemize}
  \item Applications Engineer
  \item Automation Consultant
  \item Controls Engineer
\end{itemize}

\newpage
\subsection*{Core responsibilities}
\begin{itemize}
  \item Strengthen customer relationships and contribute to Siemens' growth and reputation.
  \item U.S. work authorization with no sponsorship
  \item willing to commit to required moves.
  \item Strong programming foundation (IEC 61131-3 Ladder Logic, C\#, Python, C/C++, Java, mobile/web, PLCs/HMIs).
  \item (Preferred) Leadership experience (academic or extracurricular).
  \item (Preferred) Strong communication skills and customer focus.
  \item (Preferred) Ethernet networking, statics/dynamics, Windows app development
  \item \textbf{Industrial Networking:} The methods for connecting automation devices (like PLCs, VFDs, and robots) to ensure reliable communication.
  \item \textbf{Cybersecurity:} The protection of industrial control systems from cyber threats.
  \item \textbf{Functional areas}: software/hardware architecture design, testing, project management, electromechanical Systems
  \item \hrulefill
  \item (Preferred/not qualified) Internship or project experience in industrial/manufacturing environments.
  \item (Preferred/not qualified) Basic understanding of control theory and/or PLCs.
  \item \textbf{Control Theory:} The study of how to manipulate the parameters affecting the behavior of a dynamic system.
  \item (Preferred/not qualified) power electronics, motion control, CNC, robotics.
  \item \textbf{Programmable Logic Controllers (PLCs):} The central control units for automation, used to manage machinery and processes.
  \item \textbf{Variable Frequency Drives (VFDs):} Devices used for controlling the speed of electric motors, which are critical for machine control and energy efficiency.
  \item \textbf{Computer Numerical Control (CNC):} Automation systems specifically for machine tools, such as mills, lathes, and routers.
  \item \textbf{Digital IIoT Technology:} The application of the Industrial Internet of Things (IIoT) to gather and analyze data from the factory floor.
  \item Design and implement technical solutions using factory automation, motion control, process automation, and simulation tools.
  \item Consult with customers to drive digital transformation via IIoT, additive manufacturing, digital drive trains, and robotics.
\end{itemize}

In these roles, individuals are responsible for consulting with Siemens' customers, designing custom software and hardware solutions, and assisting companies with the implementation of smart factory and digital transformation initiatives using Siemens technology.




\end{document}